### 2019-11-18 README.Rmd
Update README.Rmd

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer) [![Travis-CI Build Status](https://travis-ci.org/tidymodels/infer.svg?branch=master)](https://travis-ci.org/tidymodels/infer) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/tidymodels/infer?branch=master&svg=true)](https://ci.appveyor.com/project/tidymodels/infer) [![Coverage Status](https://img.shields.io/codecov/c/github/tidymodels/infer/master.svg)](https://codecov.io/github/tidymodels/infer/?branch=master)

@@

To install the cutting edge version of `infer` (do so at your own risk), make sure to install `remotes` first. This version was last updated on `r Sys.time()`.

>>>>

[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer) [![Travis-CI Build Status](https://travis-ci.org/tidymodels/infer.svg?branch=master)](https://travis-ci.org/tidymodels/infer) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/tidymodels/infer?branch=master&svg=true)](https://ci.appveyor.com/project/tidymodels/infer) [![Coverage Status](https://img.shields.io/codecov/c/github/tidymodels/infer/master.svg)](https://codecov.io/github/tidymodels/infer/?branch=master)

@@

To install the cutting edge version of `infer` (do so at your own risk), make sure to install `remotes` first.
